Turbulence in compact to giant HII regions

### 2022-02-23 strucfunc_paper.tex
Describe seeing

We also take into account in the new functional observational constraints like the seeing and observational box size (see Appendix~\ref{sec:degr-struct-funct} for details).

The seeing becomes important at small scales and it is known that has an effect giving a more pronounced stepping in the structure function.
The model proposed to describe the seeing at small scales is:
%
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  }
\end{equation}

>>>>

Two observational effects can modify the observed structure function at the smallest scales.
On the one hand, the blurring of the observed image by atmospheric seeing
tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile.\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
}
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
Note that the effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 s_0\).
